Testing Quasar Unification: I. Radiative Transfer in Clumpy Winds

### 2016-02-01 paperbold.tex
added paperbold

Our kinematic prescription for a biconical disc wind model
follows \cite{SV93}, and is described further by
LK02, H13 and M15. {\bf We emphasise that the purpose of this
purely kinematic wind model is to provide a simple tool for 
exploring different outflow geometries and kinematics.}
A schematic is shown in Fig.~\ref{fig:cartoon},
with key aspects marked. The general biconical
geometry is similar to that invoked by \cite{MCGV95} and 
\cite{elvis2000} to explain the phenomenonology
of quasars and BALQSOs. {\bf However, we do not include the initial
vertical component present in the Elvis (2000) model, which was
invoked as a qualitative explanation for narrow absorption lines}.

@@

\begin{figure*}
\centering
\includegraphics[width=0.8\textwidth]{figures/fig7.eps}
\caption
{
\civ , \mg , \al\ and Fe~\textsc{ii} line profiles for viewing angles
from $72-79^\circ$. The profiles are plotted relative to the local
continuum with an offset applied for clarity. Lower ionization
profiles appear at a subset of high inclinations, compared
to the ubiquitous \civ\ profile.
}
\label{fig:lobal}
\end{figure*}

@@

%% \texttt{mn2e.cls} \textsc{Latex} document class.

\bibliography{bibs/mybib.bib,bibs/stellar.bib,bibs/h14.bib,bibs/h13.bib,bibs/hamann.bib,bibs/krolik.bib}

>>>>

Our kinematic prescription for a biconical disc wind model
follows \cite{SV93}, and is described further by
LK02, H13 and M15. {\bf We emphasise that the purpose of this
purely kinematic wind model is to provide a simple tool for 
exploring different outflow geometries and kinematics, and
the model itself is not hydrodynamic.}
A schematic is shown in Fig.~\ref{fig:cartoon},
with key aspects marked. The general biconical
geometry is similar to that invoked by \cite{MCGV95} and 
\cite{elvis2000} to explain the phenomenonology
of quasars and BALQSOs. {\bf However, we do not include the initial
vertical component present in the Elvis (2000) model, which was
invoked as a qualitative explanation for narrow absorption lines}.

@@

\begin{figure*}
\centering
\includegraphics[width=1.0\textwidth]{figures/fig7.eps}
\caption
{
\civ , \mg , \al\ and Fe~\textsc{ii} line profiles for viewing angles
from $72-79^\circ$. The profiles are plotted relative to the local
continuum with an offset applied for clarity. Lower ionization
profiles appear at a subset of high inclinations, compared
to the ubiquitous \civ\ profile.
}
\label{fig:lobal}
\end{figure*}

@@

%% \texttt{mn2e.cls} \textsc{Latex} document class. 
\setlength{\bibsep}{0pt}
\bibliography{bibs/mybib.bib,bibs/stellar.bib,bibs/h14.bib,bibs/h13.bib,bibs/hamann.bib,bibs/krolik.bib}
